Missing The Point

### 2020-09-23 Manuscript.Rmd
Extend example with plots

## Check if heuristic for AC works
```{r}
load("~/MissingThePoint/Data/convergence_diagnostics_test.Rdata")
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == 1, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```

>>>>

## Check if heuristic for AC works
```{r}
# load("~/MissingThePoint/Data/diagnostics.Rdata")
# load("~/MissingThePoint/Data/raw_outcomes.Rdata")
sim_nr <- 3
outcomes[[sim_nr]] %>% filter(mech == "MCAR", p == 0.95) %>% ggplot(aes(x=it, y = est)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.qhat)) + geom_line()
convergence_diagnostics %>% filter(sim == sim_nr, mech == "MCAR", p ==0.95) %>% ggplot(aes(x=it, y = ac.max.lambda)) + geom_line()
```

## Example data

```{r}
load("~/MissingThePoint/Data/example.Rdata")

# plot example
plotfun <- function(v){
ggplot(example, aes(x = it, y = .data[[v]])) +
  geom_line() +
  theme_classic()
}

plotfun(v="est")
plotfun(v="ac.max.qhat")
plotfun(v="ac.max.lambda")
plotfun(v="r.hat.max.qhat")+list(geom_hline(yintercept = 1.2, color = "grey"))
plotfun(v="r.hat.max.lambda")+list(geom_hline(yintercept = 1.2, color = "grey"))

load("~/MissingThePoint/Data/example_mids.Rdata")
plot(mids)
```
